\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{framed}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{booktabs}
\usepackage{amsmath}

\marginparwidth 0.5in 
\oddsidemargin 0.25in 
\evensidemargin 0.25in 
\marginparsep 0.25in
\topmargin 0.25in 
\textwidth=6in
\textheight=8in

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolor}{rgb}{0.95,0.95,0.95}

% lstlisting setttings
\lstset{
  backgroundcolor=\color{backcolor}, % Set background color
  commentstyle=\color{codegreen}, % Style for comments
  keywordstyle=\color{magenta}, % Style for keywords
  numberstyle=\tiny\color{codegray}, % Style for line numbers
  stringstyle=\color{codepurple}, % Style for strings
  basicstyle=\ttfamily\footnotesize, % Basic font style and size
  breakatwhitespace=false, % Don't break lines at whitespace only
  breaklines=true, % Enable line breaking
  captionpos=b, % Caption position (bottom)
  keepspaces=true, % Keep spaces
  numbers=left, % Show line numbers on the left
  numbersep=5pt, % Separation of numbers from code
  showspaces=false, % Don't show spaces as visible characters
  showstringspaces=false, % Don't show spaces in strings
  showtabs=false, % Don't show tabs as visible characters
  tabsize=2, % Tab size
  language=Java% Specify the language
}

\begin{document}
\hfill\vbox{\hbox{Jude Shin}
		\hbox{CSC 369, Section 01}	
		\hbox{Assignment 2}	
		\hbox{\today}}\par

\bigskip
\centerline{\Large\bf Assignment 2}\par
\bigskip

\begin{enumerate}
	\item Consider an input file with the following example input. 

\begin{lstlisting}
John Back, 23, B, CSC366
Bob Wilson, 11, B, CS201
John Back, 23, A, CSC369
\end{lstlisting}

		In general, the input file will contain the student name, the student ID 
		number, grade, and course. You need to write a Map/Reduce program that 
		prints the student name, student id, and the list of classes for that 
		student. The output should be sorted by name and then sorted by grade for 
		each name. Here is an example output. 

\begin{lstlisting}
Bob Wilson, 11, (B, CS201)
John Back, 23, (A, CSC369), (B, CSC366) // sorted by name and then by grade
\end{lstlisting}

		\begin{enumerate}
			\item What is the natural and the composite key?

				\textit{}

			\item Show the composite key class (must implement WritableComparable and 
				have compareTo method).

\begin{lstlisting}
\end{lstlisting}

			\item Show the mapper class.

\begin{lstlisting}
\end{lstlisting}

			\item Show the partitioner class.

\begin{lstlisting}
\end{lstlisting}

			\item Show the group comparator class.

\begin{lstlisting}
\end{lstlisting}

			\item Show the reducer class.

\begin{lstlisting}
\end{lstlisting}
		\end{enumerate}
\end{enumerate}

\end{document}
